Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-14 chi2012.tex
Adding images into document

>>>>

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=18cm]{img/dragdrop}
\caption{WebBox uses a Drag and Drop interface to add data into the workspace.}
\label{fig:dragdrop}
\end{center}
\end{figure*}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{img/multipathing}
\caption{To see properties, users click on the name of the property. When instances do not have a particular property, additional property names can be added.}
\label{fig:multipathing}
\end{center}
\end{figure}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=18cm]{img/sameas}
\caption{When two instances represent the same entity, users can drag one on top of the other, and they are combined.}
\label{fig:sameas}
\end{center}
\end{figure*}
